Maximum Entropy Spectral Analysis: a case study

### 2021-03-02 paper/mesa.tex
some notes

\begin{itemize}
\item \textbf{Final prediction Error } 
The first criterion is due to Akaike~\cite{Akaike1970StatisticalPI}. He proposed that $m$ should be chosen as the 
length that minimises the error when the filter is used as a predictor, the \emph{final prediction} error (FPE): 
\begin{equation}
    FPE(m) = \mathbb{E}\left[ \left((x_t - \hat x_t) ^ 2\right) \right]
\end{equation}
with $\hat{x}_t = \sum_{i = 1}^M a_i x_{t - i}$.
Minimizing FPE is equivalent to minimizing the quantity: 
\begin{equation}
    \mathcal{L}_{\rm FPE}(m) = P_{m} \frac{N + m + 1}{N - m - 1}
\end{equation}
with $P_m$ defined by the prediction error filter equation \sschmidt{What is this equation?}.
\item \textbf{Criterion Autoregressive Transfer function (CAT)}
This second loss function is due to Parzen~\cite{bhansali1986}, and it is defined as
\begin{equation}
    \mathcal{L}_{\rm CAT}(m) = \frac{1}{N}\sum_{k = 1}^m \frac{N - k}{N P_k} - \frac{N - m}{N P_m}.
\end{equation}
It has the interesting property that the distance between the original filter and the estimate is minimum and asymptotically unbiased. \wdp{please expand}

\item \textbf{Optimum Bayes Decision rule} 
The last criterion we will consider is the Optimum Bayes Decision rule (OBD)\cite{doi:10.1029/WR018i004p01097}. With the technique of asymptotic integration, the loss function is proposed to be the length that maximizes the posterior distribution \sschmidt{Which posterior?}: 
   \begin{align}
        \mathcal{L}_{\rm OBD}&(m) = (N - m - 2) \log(P_m) \nonumber\\
        &+ m \log(N) + \sum_{k = 0}^{m-1} \log(P_k) + \sum_{k = 1}^{m} a_k^2\,.
    \end{align}
\end{itemize}

>>>>

\begin{itemize}
\item \textbf{Final prediction Error } 
The first criterion is due to Akaike~\cite{Akaike1970StatisticalPI}. He proposed that $m$ should be chosen as the 
length that minimises the error when the filter is used as a predictor, the \emph{final prediction} error (FPE): 
\begin{equation}
    FPE(m) = \mathbb{E}\left[ \left((x_t - \hat x_t) ^ 2\right) \right]
\end{equation}
with $\hat{x}_t = \sum_{i = 1}^M a_i x_{t - i}$.
Minimizing FPE is equivalent to minimizing the quantity: 
\begin{equation}
    \mathcal{L}_{\rm FPE}(m) = P_{m} \frac{N + m + 1}{N - m - 1}
\end{equation}
with $P_m$ defined by the prediction error filter equation \sschmidt{What is this equation?}.
\wdp{comment on N that goes to infinity, just minimising the variance of the process}
\item \textbf{Criterion Autoregressive Transfer function (CAT)}
This second loss function is due to Parzen~\cite{bhansali1986}, and it is defined as
\begin{equation}
    \mathcal{L}_{\rm CAT}(m) = \frac{1}{N}\sum_{k = 1}^m \frac{N - k}{N P_k} - \frac{N - m}{N P_m}.
\end{equation}
It has the interesting property that the distance between the original filter and the estimate is minimum and asymptotically unbiased. \wdp{please expand}

\item \textbf{Optimum Bayes Decision rule} 
The last criterion we will consider is the Optimum Bayes Decision rule (OBD)\cite{doi:10.1029/WR018i004p01097}. With the technique of asymptotic integration, the loss function is proposed to be the length that maximizes the posterior distribution \sschmidt{Which posterior?}, \wdp{please check this equation}: 
   \begin{align}
        \mathcal{L}_{\rm OBD}&(m) = (N - m - 2) \log(P_m) \nonumber\\
        &+ m \log(N) + \sum_{k = 0}^{m-1} \log(P_k) + \sum_{k = 1}^{m} a_k^2\,.
    \end{align}
\end{itemize}
